Growing Up With Nell: A Narrative Interface for Literacy

### 2012-04-23 paper.tex
Space-saving hacks.
Remove Weizenbaum cite, since Turkle mentions this in the previous citation
and Weizenbaum doesn't really talk much about Eliza in the cited book.

Remove middle initial from E. H. Stefanakis in order to fit citation onto
two lines instead of three.

\subsection{Extensible dialog}
Nell's use as an interactive diary and
\textit{portfolio}~\cite{stefanakis:portfolios} is enhanced by the child's
collaboration in the fiction that Nell is intelligent---what
Turkle~\cite{turkle:alone} calls the ``ELIZA effect.''
Convincing discourse is a hard problem, but
reasonable approximations do not have to be difficult; even
the rudimentary conversational abilities of ELIZA elicited hours of
conversation~\cite{weizenbaum:power}.
% her secretary is divulging her life story
% asks him to leave the room so he could be alone with it
% hours discussing her boyfriend.
We've chosen to allow the child to directly converse with the
Princess and other agents within Nell.

\begin{figure}\small
\begin{verbatim}
{ "aiml": {
  "version": "1.0",
  "categories": [
    { "pattern": "GO *",
      "template": "{*}" },
    { "pattern": "N",
      "template": "{NORTH}" },
    { "pattern": "NORTH",
      "template": js`FireEvent(Chat, "NORTH")` },
    { "pattern": "* THE DOOR",
      "template": "{*} DOOR" },
    { "pattern": "* SQUEAKY DOOR",
      "template": "{*} DOOR" },
    { "pattern": "OPEN DOOR",
      "template": js`FireEvent(Chat, "OPEN DOOR")` }
  ] } }
\end{verbatim}
% alternate template syntax, compatible w/ quasiquote but not
% dependent on it:
% template: "${srai(star(0))}" // can be abbreviated as srai(star()) or srai()
% template: "${srai("NORTH"}}"
% template: "${FireEvent(Chat, "NORTH")}"
% template: "${srai()} DOOR" // abbreviation for srai(star(0))
\caption{An AIML fragment which recognizes the commands
  %\texttt{N},
  \texttt{North}, \texttt{Go North}, \texttt{Open the squeaky door}
  and variants.  AIML's XML syntax has been translated to JSON.
  Template contents in braces invoke the recognizer recursively
  (what AIML calls \texttt{<srai>}).
% XXX: how to handle multiple stars?  In XML, it's <star index="1">
}\label{fig:aiml}
\end{figure}

>>>>

\subsection{Extensible dialog}
Nell's use as an interactive diary and
\textit{portfolio}~\cite{stefanakis:portfolios} is enhanced by the child's
collaboration in the fiction that Nell is intelligent---what
Turkle~\cite{turkle:alone} calls the ``ELIZA effect.''
Convincing discourse is a hard problem, but
reasonable approximations do not have to be difficult; even
the rudimentary conversational abilities of ELIZA elicited hours of
conversation.%~\cite{weizenbaum:power}
% her secretary is divulging her life story
% asks him to leave the room so he could be alone with it
% hours discussing her boyfriend.
We've chosen to allow the child to directly converse with the
Princess and other agents within Nell.

\begin{figure}\small
% (could remove
%  "version": "1.0",
% before "categories" in order to save space in paper)
\begin{verbatim}
{ "aiml": {
  "version": "1.0",
  "categories": [
    { "pattern": "GO *",
      "template": "{*}" },
    { "pattern": "N",
      "template": "{NORTH}" },
    { "pattern": "NORTH",
      "template": js`FireEvent(Chat, "NORTH")` },
    { "pattern": "* THE DOOR",
      "template": "{*} DOOR" },
    { "pattern": "* SQUEAKY DOOR",
      "template": "{*} DOOR" },
    { "pattern": "OPEN DOOR",
      "template": js`FireEvent(Chat, "OPEN DOOR")` }
  ] } }
\end{verbatim}
% alternate template syntax, compatible w/ quasiquote but not
% dependent on it:
% template: "${srai(star(0))}" // can be abbreviated as srai(star()) or srai()
% template: "${srai("NORTH"}}"
% template: "${FireEvent(Chat, "NORTH")}"
% template: "${srai()} DOOR" // abbreviation for srai(star(0))
\caption{An AIML fragment which recognizes the commands
  %\texttt{N},
  \texttt{North}, \texttt{Go North}, \texttt{Open the squeaky door}
  and variants.  AIML's XML syntax has been translated to JSON.
  Template contents in braces invoke the recognizer recursively
  (what AIML calls \texttt{<srai>}).
% XXX: how to handle multiple stars?  In XML, it's <star index="1">
}\label{fig:aiml}
\end{figure}
